### 2019-12-21 Statistical Methods/07_hypothesis-testing.rmd
statistical methods
statistical methods

### 7.11
### 7.12
### 7.13
### 7.14
### 7.15
### 7.16
### 7.17
### 7.18
### 7.19

>>>>

### 7.11

An antipollution device for cars is claimed to have an average effectiveness of exactly 546. Based on a test of 20 such devices, you find that $\bar{X} = 565$.

Assuming normality and that $\sigma = 40$, would you rule out the claim with a Type I error probability of 0.05?

```{r, echo = T}
xbar <- 565; sigma <- 40; n <- 20
alpha <- 0.05; h0 <- 546

# equality = two tailed

crit <- qnorm(c(alpha/2, 1 - alpha/2))

ifelse(Z < crit[1] || Z > crit[2], "Reject the null", "Cannot reject the null")
```

### 7.12

Comment on the relative merits of using a 0.95 confidence interval for addressing the effectiveness of the antipollution device in the previous exercise rather than test the hypothesis: $H_0 : \mu = 232$

```{r, echo = T}
xbar + qnorm(c(alpha/2, 1 - alpha/2)) * sigma/sqrt(n)

2 * ( 1 - pnorm(Z) )
```

The hypothesised value doesn't fall within the confidence interval, however the formalized test gives us a degree of strength on which we can reject the null. Here our p-value is .03, so we reject with confidence.

### 7.13

### 7.14
### 7.15
### 7.16
### 7.17
### 7.18
### 7.19
